%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sourish Mandal} \\ \vspace{1pt}
    \small (91)747-917-7464 $|$
    \href{mailto:sourishmandaldgp@gmail.com}{\underline{sourishmandaldgp@gmail.com}} $|$
    \href{mailto:btech15026.20@bitmesra.ac.in}{\underline{btech15026.20@bitmesra.ac.in}} $|$ 
    \href{https://linkedin.com/in/sourish-mandal}{\underline{linkedin.com/in/sourish-mandal}} $|$
    \href{https://github.com/sourish-m}{\underline{github.com/sourish-m}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Birla Institute of Technology Mesra}{Ranchi, Jharkhand}
      {Bachelor of Technology in Computer Science and Engineering, GPA:9.05}{Aug. 2020 -- May 2024}
    \resumeSubheading
      {DAV Model School}{Durgapur, West Bengal}
      {Higher Secondary, 92.6\% in Boards}{2018 -- 2020}
    \resumeSubheading
      {St. Peter’s School}{Durgapur, West Bengal}
      {Secondary, 97.2\% in Boards}{-- 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{June 2023 -- August 2023}
      {National Institute of Technology Patna}{Patna, Bihar}
      \resumeItemListStart
        \resumeItem{Collaborated as part of a 2-member team to conduct a research project on \"Zero-day attack detection using FP-Growth algorithm\".}
        \resumeItem{Developed an innovative technique to detect unknown vulnerabilities in network.}
        \resumeItem{Successfully designed and implemented a functional model using Python, NumPy, Pandas and Bash that achieved an accuracy rate of 91.6\%.}
        \resumeItem{Key Skills: Machine Learning, Cybersecurity, Data Mining and Analysis}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Library Management System} $|$ \emph{Python, Flask, Javascript, SQLite}}
          \resumeItemListStart
            \resumeItem{Developed a robust full stack Library Management system website utilizing Flask and 
SQLalchemy.}
            \resumeItem{Used Bulma CSS Framework for the frontend.}
            \resumeItem{Integrated external book data API.}
            \resumeItem{Designed efficient CRUD operations across multiple database tables.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Customer Analysis Simulation (Forage)} $|$ \emph{Python}}
          \resumeItemListStart
            \resumeItem{Completed a customer churn analysis simulation, demonstrating advanced data analytics skills, identifying essential client data and outlining a strategic investigation approach.}
            \resumeItem{Completed the engineering and optimization of a random forest model with 85\% accuracy. Created a concise executive presentation, delivering insights for informed decision-making.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{To-Do List App} $|$ \emph{Kotlin, Material-UI}}
          \resumeItemListStart
            \resumeItem{Developed a simple To-do List App for Android.}
            \resumeItem{Used Material UI design and latest Android coding guidelines.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (MySQL), JavaScript, HTML/CSS, Kotlin} \\
     \textbf{Frameworks}{: Flask, Bulma} \\
     \textbf{Developer Tools}{: Git, Github Actions, Linux, Bash Scripting} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}

 \section{Extra-Curricular Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Student Board Member}{: Served as the liaison between students and teacher body. Forwarded problems faced by students to the school board. Worked on the student committee elections, leading junior volunteers in conducting a proper voting process. Participated in regular board meetings and committees to discuss and vote on school policies, budget, curriculum, and other matters} \\
     }}
 \end{itemize}


%-------------------------------------------
\end{document}
